Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-18 WRITEUP/ms.tex
edited caption MR relation

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with MW-like dust can be written as 
\begin{equation}
A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
then, assuming spherical symmetry, the mass of a MC can be expressed as a function of $A_v$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154 \,A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we have taken $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(r/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
\label{fig:MR}}
\end{figure*}

@@

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
an ``internal'' mass-size relation where $M\propto r^{1.33}$.
If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
regions of high-mass \SF. That is, the MCs identified have mass-size relations suggesting they are capable of high-mass \SF.

>>>>

% ------------------
\section{Numerical simulations}\label{sec:sim}
The simulations used in this work are described by \citealt{Pallottini17a, Pallottini17b} and are only briefly summarized here.
%
\ncode{Serra}\footnote{Greenhouse in italian} is a suite of cosmological zoom-in simulations performed using Eulerian hydrodynamics and adaptive mesh refinement (AMR) technique to achieve high spatial resolution in the region of interest (i.e., regions of high density).
%
In particular, it uses a modified version of \ncode{ramses} \citep{Teyssier02a} as the AMR backend. The simulation used here covers a comoving box of 20\,Mpc $h$\pmOne in size, resolving down to a physical scale of $l_{\rm cell}\approx$\,30\,pc (at $z\sim6$) and a (baryonic) mass resolution of $m_b\simeq$\,10$^4$\,\Msun at the finest level. Such a physical scales are comparable to those of local giant molecular clouds \citep[e.g.,][]{Sanders85a, Federrath13a, Goodman14a}.

@@

% cloud structures at large and small scale
% Larson's: m = 460 M_sun (r_pc)^1.9 for structure w/in molecular clouds. --> $m \propto r^2$ \citep{McKee07a} (law of constant
% column density) as fundamental properties of molecular cloud structure.
Larson's third relation relates MCs structures on small and large scales via two physical properties: mass and size \citep{Larson81a, McKee07a}. This is also known as the constant column density relation, since cloud mass in \obs is sometimes derived by integrating over the mass surface density, which is related to the column density ($N_H$) obtainable from extinction maps ($A_V$). By assuming dust properties from \citet[][]{weingartner:2001}, extinction for a cloud with Milky Way-like dust can be written as 
\begin{equation}
A_v = \frac{N_H}{1.8 \times 10^{21} {\rm cm}^{-2}}\,,
\end{equation}
then, assuming spherical symmetry, the mass of an MC can be expressed as a function of $A_v$ and its size $R$
\begin{equation}\label{eqn:constantcolumndensity}
M_{\rm cl} = \frac{4\pi}{3} \mu m_p n R^3 = 154~A_v \left(\frac{R}{\rm pc}\right)^2 \Msun \,,
\end{equation}
where we have taken $\mu = 2.5$ as the mean molecular weight.

We show in \Fig{MR} the size-mass relation of the MCs of \flower compared to observational data of molecular clouds in the Milky Way that are found to be associated with massive \SF \citep{Beuther02a, Mueller02a, Hill05a, Motte07a} and an empirical relation obtained for massive \SF based on Milky Way clouds ($<$10\,\Msun; \citealt{Kauffmann10b, Kauffmann10c} and references therein): $M \gtrsim 870$\,\Msun$\times\,\left(R/{\rm pc}\right)^{1.33}$.
%
In the same plot, we also show loci of constant surface densities, which are parameterized through the visual extinction $A_V$. As shown in \Fig{MR}, the MCs identified in \flower lie above this relation, along the locus of $A_v \simeq 8.9$ clouds observed by \citet{Lombardi10a} in the MW.
%
%The values of $A_V$ inferred from http://adsabs.harvard.edu/abs/2017MNRAS.471.5018Fthe $M_{\rm cl}$-size relation is consistent with the extinction inferred from gas clumps analysing the UV and IR emission of \flower~by calculating the effect of radiative transfer through dust \citep[][in particular see Fig. 5 therein]{Behrens18a}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.8\textwidth]{\figpath/lf16_cloud-mass_size-pc.png}
\caption{
Size-mass relation of MCs identified in the accretion phase of \flower in our simulation (star symbols) compared to observational data of molecular clouds in the Milky Way associated with massive \SF (magenta circles, green stars, blue dots, and black triangles) and empirical relations established based on \obs of the Milky Way. Red line shows the 
mass-size relation found for regions in the Milky Way with massive \SF reported by \citet{Kauffmann10b}. Star symbols are color-coded by increasing $n_{\rm cut}$. Literature data are compiled from \citet{Beuther02a, Mueller02a, Hill05a, Motte07a}. 
Colored lines show the loci expected for different visual extinctions ($A_V$, see \Eq{constantcolumndensity}), which correspond to lines of
constant surface density (i.e., Larson's third relation). This representation is motivated by observational studies (see text and e.g., \citealt{Lombardi10a}).
The star symbols are color-coded by $n_{\rm cut}$, same as \Fig{larsons_single}. 
Extrapolating the masses and sizes of MCs of \flower along the \citet{Kauffmann10b} 
relation down to 1\,pc are comparable  to those  of  the  cores  found  in regions  of high-mass star formation, suggesting that the identified MCs are capable of high-mass \SF.
\label{fig:MR}}
\end{figure*}

@@

The \citet{Kauffmann10c} relation suggests that regions with high-mass \SF follow 
an ``internal'' mass-size relation where $M\propto R^{1.33}$.
If this holds for MCs of \flower, an extrapolation of the \citet{Kauffmann10c} relation down to $\sim$1\,pc would correspond to structures with masses and sizes comparable to those of the cores found in
regions of high-mass \SF. That is, the MCs identified have mass-size relations suggesting they are capable of high-mass \SF.
